High-Dimensional Regularized Discriminant Analysis

### 2017-10-17 reports/paper-hdrda.Rnw
scratch that. postscript is smaller and converts to PDF automatically

opts_chunk$set(fig.align='default', dev=c("tiff", "png"),
               message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, autodep=TRUE,
               dpi=300, fig.width=12, fig.height=12, out.width="\\linewidth")
@

>>>>

opts_chunk$set(fig.align='default', dev="postscript",
               message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, autodep=TRUE,
               dpi=300, fig.width=12, fig.height=12, out.width="\\linewidth")
@
